Modelling at-bats in baseball using the generalised Pareto distribution

### 2023-05-23 bibat/examples/baseball/docs/report.qmd
Fix mistakes in baseball vignette

I thought I'd test this out with some sports data, and luckily there is a really
nice baseball example on [the Stan case studies
website](https://mc-stan.org/users/documentation/case-studies/pool-binary-trials.html),
complete with [data from the 2006 Major league
season])https://github.com/stan-dev/example-models/blob/master/knitr/pool-binary-trials/baseball-hits-2006.csv).
After I posted some early results [on the Stan discourse
forum](https://discourse.mc-stan.org/t/baseball-analysis-using-latent-generalised-pareto-distribution/29222),
other users suggested that it might be interesting to model similar data from
different seasons. This data can now be found quite easily on the [baseball
databank](https://baseballdb.lawlesst.net/).

@@

```{.python include="../baseball/data_preparation.py" start-line=101}
```

@@

```{.python include="../baseball/data_preparation.py" start-line=33 end-line=52}
```

To finish off I deleted the unused global variables `MEASUREMENTS_FILE`,
`NEW_COLNAMES`, `DROPNA_COLS` and `DIMS`, then checked if the function
`load_prepared_data` needed any changes: I was pretty sure it didn't.

>>>>

I thought I'd test this out with some sports data, and luckily there is a really
nice baseball example on [the Stan case studies
website](https://mc-stan.org/users/documentation/case-studies/pool-binary-trials.html),
complete with [data from the 2006 Major league
season](https://github.com/stan-dev/example-models/blob/master/knitr/pool-binary-trials/baseball-hits-2006.csv).
After I posted some early results [on the Stan discourse
forum](https://discourse.mc-stan.org/t/baseball-analysis-using-latent-generalised-pareto-distribution/29222),
other users suggested that it might be interesting to model similar data from
different seasons. This data can now be found quite easily on the [baseball
databank](https://baseballdb.lawlesst.net/).

@@

```{.python include="../baseball/data_preparation.py" start-line=103}
```

@@

```{.python include="../baseball/data_preparation.py" start-line=35 end-line=53}
```

To finish off I deleted the unused global variables `NEW_COLNAMES`,
`DROPNA_COLS` and `DIMS`, then checked if the function `load_prepared_data`
needed any changes: I was pretty sure it didn't.
